Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Fix syntax for multiple parenthetical citations

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology 
[@gonzales2010language, @tausczik2010psychological, @brennan1996conceptual]; 
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative, @fusaroli2015timescales]. 
This kind of massive online social cohesion can lead to real-world
social change.

>>>>

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology 
[@gonzales2010language; @tausczik2010psychological; @brennan1996conceptual]; 
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative; @fusaroli2015timescales]. 
This kind of massive online social cohesion can lead to real-world
social change.
